Copykat CNV results exploration for `r params$sample_id`

### 2024-10-18 analyses/cell-type-wilms-tumor-06/notebook_template/05_copykat_exploration.Rmd
Update analyses/cell-type-wilms-tumor-06/notebook_template/05_copykat_exploration.Rmd
Co-authored-by: Stephanie Spielman <stephanie.spielman@gmail.com>

  - Visualize diploid and aneuploid cells on the UMAP. 
  - Evaluate common copy number gains and losses in Wilms tumor. 
  - Calculate the confusion matrix comparing manual annotations of tumor cells to using `CopyKAT` to annotate tumor cells. 
  - Compare the annotations from `CopyKAT` to cell type annotations using label transfer and the fetal (kidney) references.

@@

From the heatmap of CNV and the mean CNV detection plots, it is difficult to see any CNV pattern that drive the identification of aneuploid cells. 
The assignment of the aneuploidy/diploidy value might relies on very few CNV and/or an arbitrary threshold. 
This might be why the assignement of aneuploidy/diploidy values differs between condition (and between runs!!).

>>>>

  - Visualize diploid and aneuploid cells on the UMAP. 
  - Evaluate common copy number gains and losses in Wilms tumor. 
  - Compare the annotations from `CopyKAT` to cell type annotations using label transfer and the fetal (kidney) references.

@@

From the heatmap of CNV and the mean CNV detection plots, there does not appear to be any pattern that drives the identification of aneuploid cells. 
The assignment of the aneuploidy/diploidy value might relies on very few CNV and/or an arbitrary threshold. 
This might be why the assignement of aneuploidy/diploidy values differs between condition (and between runs!!).
